Computer Science House Constitution

### 2025-11-22 constitution.tex
dual chair bad

\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all current members of the RIT professional, academic, or administrative staff.

@@

\asubsection{Honorary Membership Term}
Honorary Membership shall last until the member resigns.

\asubsection{Advisory Membership Term}
Advisory Membership shall last until the member resigns or is no longer employed by RIT, whichever comes first.

@@

\asubsubsection{Waiving of Qualifications}
\begin{enumerate}
	\item CSH may choose to waive the following subset of the qualifications for E-Board positions, as defined under \ref{Qualifications}, for all candidates:
	      \begin{enumerate}
		      \item Candidates must reside on floor during the term of office.
		      \item Social and R\&D are the only voting E-Board positions that allow for dual directorship.
	      \end{enumerate}
	\item When a waiver is proposed, the Chair of the Vote shall state which E-Board position and qualification is being voted upon, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
	\item A Three-Quarters Immediate Vote with three-quarters quorum is then taken to determine whether the proposed waiver shall take effect.
	\item Each vote to waive a qualification must only apply to a single qualification for a single E-Board position.
	\item Waivers always apply to all candidates for the E-Board position.
\end{enumerate}

@@

\asubsubsection{Dual Directors}
Social and R\&D are the only Voting E-Board positions that allow for dual directors.

>>>>

\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the RIT professional, academic, or administrative staff.

@@

\asubsection{Honorary and Advisory Membership Term}
Honorary and Advisory Memberships shall last until the member resigns.

@@

\asubsubsection{Waiving of Qualifications}
\begin{enumerate}
	\item CSH may choose to waive the following subset of the qualifications for E-Board positions, as defined under \ref{Qualifications}, for all candidates:
	      \begin{enumerate}
		      \item Candidates must reside on floor during the term of office.
		      \item Social and R\&D are the only E-Board positions that allow for dual directorship.
	      \end{enumerate}
	\item When a waiver is proposed, the Chair of the Vote shall state which E-Board position and qualification is being voted upon, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
	\item A Three-Quarters Immediate Vote with three-quarters quorum is then taken to determine whether the proposed waiver shall take effect.
	\item Each vote to waive a qualification must only apply to a single qualification for a single E-Board position.
	\item Waivers always apply to all candidates for the E-Board position.
\end{enumerate}

@@

\asubsubsection{Dual Directors}
Social and R\&D are the only E-Board positions that allow for dual directors.
